\subsection{Problem Statement}
Dance Dance Revolution (DDR) is a video game where the player attempts to press down arrows at specific times during a song, which simulates dance. A single DDR game consists of a music file and a steps file which are parsed and rendered by the game for playing. To generate a music file and steps file pair, an experienced person would need to manually map out the song to musical dance elements and indicate at which precise moments in time each arrow would need to be hit. The entire process would take 4 or more hours. An easier way to generate new playable songs is needed so that players can enjoy dancing to their favorite songs.\\

\subsection{Goal}
The goal of this project is to create a system that automatically generates an accompanying steps file with a music file as input. The system will be implemented using neural networks and fuzzy logic and trained using existing music files and steps files. The qualitative measurement of the goal is to assess the produced steps files by their playability, and whether or not they exhibits a touch of human creativity. The quantitative measurement of the goal is the percentage of the steps that are generated which occur at the same time as recognised musical features, for example beats.\\


\subsection{DDR Game and Motivation}
Dance Dance Revolution is a rhythm game where the player hits arrows on a dance pad with their foot as the arrows come up on screen. DDR has a competitive scene where players compete with difficult songs that require more than 16 steps per second and are graded on their accuracy. The game can be played on the PC with a free downloadable emulator and has a reasonably large player base. However, the player base has failed to increase because the songs that were available for the game was very limited and new players could not play their favourite songs. The motivation for this project is to provide users with a tool that can generate DDR steps files from any song they choose. The success of this project could easily revitalise the DDR community.